---
title: "Case Study - Online Sales"
author: "Ahmet Selimhan ŞAHİN"
date: "20 11 2021"
output: html_document
---

## Homework 1
&nbsp;
&nbsp;
&nbsp;
&nbsp;

     
        
### Downloading the required packages

```{r , warning=FALSE , message=FALSE}
## Messages and warnings are suspended to prevent reader to be disturbed
library(knitr)
library(ggplot2)
library(rworldmap)
library(dplyr)


```

   
    
    
    
```{r , warning=FALSE , message=FALSE}
load("F:/ders/3rd_class/IE421 Data Science for Engineers/week6/salesData.Rdata")
```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
                     
                     
                           

## Question 1 Visualizing Number of Invoices
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
                        
                        

```{r , warning=FALSE , message=FALSE}
invoiceData = salesData %>%
  group_by(InvoiceNo , Country) %>%
  summarize(
    count = n()
  )

invoiceData
```





```{r , warning=FALSE , message=FALSE}
invoiceData %>%
  filter(Country != "United Kingdom") %>%
  ggplot() + geom_bar(mapping = aes(reorder(Country , table(Country)[Country])) , fill = "steelblue") + 
  labs(x = "Country" , y = "Number of Invoices" , title = "Number of Invoices from non-UK Orders") + coord_flip()


```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

## Question 2 Total Revenue from Countries

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
```{r , warning=FALSE , message=FALSE}
TotalPrice = mutate(salesData , TotalPrice = 
                      Quantity * UnitPrice)
head(TotalPrice , 15)

```



```{r , warning=FALSE , message=FALSE}
top10_countries = TotalPrice %>%
  group_by(Country) %>%
  summarize(
    countrywise_totalrevenue =         sum(TotalPrice) ) %>%
  arrange(desc(countrywise_totalrevenue)) %>%
  top_n(n = 10 , wt = countrywise_totalrevenue)
   
top10_countries  
  

```




```{r , warning=FALSE , message=FALSE}
kable(top10_countries , align = c("c" , "c") , col.names = c("Country" , "Total Revenue") , caption = "Top 10"  )


```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
## Top 10 Countries on the Map
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
```{r , warning=FALSE , message=FALSE}
n <- joinCountryData2Map(top10_countries , joinCode = "NAME" , nameJoinColumn = "Country")
```

```{r , warning=FALSE , message=FALSE}
mapCountryData(n , nameColumnToPlot = "countrywise_totalrevenue" , mapTitle = "Top 10 Countries Based on total revenue")


```


```{r , warning=FALSE , message=FALSE}
mapCountryData(n , nameColumnToPlot = "countrywise_totalrevenue" , mapRegion = "Europe" , mapTitle = "top European ")


```

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
## Question 3  Most Valued Products and Customers

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
```{r , warning=FALSE , message=FALSE}
TotalPrice %>%
  group_by(Description) %>%
  summarize(
    count = n()
  )


```









```{r , warning=FALSE , message=FALSE}
data_named = TotalPrice %>%
  group_by(Description) %>%
  summarize(
    value_product = sum(TotalPrice)) %>%
  arrange(desc(value_product)) %>%
  top_n(n = 20, wt = value_product)

kable(data_named , align = c("c" , "c") , col.names = c("Product" , "Value") , caption = "Top 20")


```
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;

## Number of Customers

&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
&nbsp;
```{r , warning=FALSE , message=FALSE}
TotalPrice %>%
  group_by(CustomerID) %>%
  summarize(
    count = n()
  )


```















```{r , warning=FALSE , message=FALSE}
top20_cust = TotalPrice %>%
  group_by(CustomerID) %>%
  summarize(customer_amount = sum(TotalPrice)) %>%
  arrange(desc(customer_amount)) %>%
  top_n(n = 20 , wt = customer_amount)


kable(top20_cust , align = c("c" , "c"))



```




















